Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-06-14 manuscript/appendix.Rmd
worked through Helene's comments in appendix
all comments are now either dealt with or represented in issues.
closes #82

\blandscape
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model details and R2 values for all climate variables tested") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=2, "MAT"=2, "MAP"=2, "T Seas"=2, "P Seas"=2, "ATR"=2, "Solar R"=2, "AI"=2))
```

>>>>

\blandscape
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/r2_table1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S2. Model form, delta AIC, and R2 for each climate variables as a single fixed effect in models for each C flux. Model forms include first-order linear (Lin), second-order polynomial (Poly), and logarithmic (Log).") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" ", "Latitude"=2, "MAT"=2, "MAP"=2, "T Seas"=2, "P Seas"=2, "ATR"=2, "Solar R"=2, "AI"=2))
```
